### 2025-07-17 paper/sections/other/main_results.qmd
table updates

>>>>

df = Serialization.deserialize("paper/experiments/output/final_table.jls")
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
formatters = (
    PrettyTables.ft_round(1,findall(.!contains.(names(df),"Acc"))),
    PrettyTables.ft_round(2,findall(contains.(names(df),"Acc")))
)
for fname in ["paper/quarto_aaai/tables/main.tex","paper/preprint/tables/main.tex"]
    tabulate_results(
        inputs; 
        table_type=:tabular, 
        save_name=fname, 
        wrap_table=false, 
        alignment=[:l,fill(:r,size(df,2)-1)...],
        formatters=formatters
    )
end
```

### Robust Performance Plots

```{julia}
plt = CTExperiments.plot_performance(res_dir, eps=range(0.0, 0.1, length=10) |> collect, adversarial=true, byvars=["objective", "eps"]) |>
    plt -> draw(plt, figure=(size=(800, 190),), axis=(yticks=[0.0,0.5,1.0], limits=(nothing, (0,1)), xticklabelsvisible=false, xticksvisible=false))
save("paper/figures/acc.png", plt; px_per_unit=3)
```
